Time invariant analysis of epidemics with \pkg{EpiCompare}

### 2021-05-10 jss/EpiCompare-paper/EpiCompare-paper.tex

In this section, we present the tools implemented in \pkg{EpiCompare}
and explain how they aid in the data analysis pipeline. In Fig.
\ref{fig:pipeline2}, we illustrate how our package's functions fit into
the data analysis pipeline introduced in Fig. \ref{fig:pipeline}. All
front-facing functions are aimed to be as user-friendly as possible. We
also focus on providing the user ``tidyverse'' style functions, that
encourage piping objects from one function to the next and follow clear
``verb'' naming schemes \citep{Wickham2019}. Although users can
incorporate \pkg{EpiCompare} into any step in the data analysis
pipeline, there are two primary points of entry. The first point of
entry is the very beginning with pre-processing and visualizing raw
data, and the second point of entry is after modeling and simulation.
Figure \ref{fig:pipeline2} captures these different paths, and we
highlight\footnote{\textcolor{violet}{[Ben says: we need to make sure we actually do highlight ]}}
both approaches and how to leverage \pkg{EpiCompare} in the subsections
below.

@@

The first step of most data analysis is ``cleaning'' the data
\textcolor{orange}{to a format that is friendly for both computers and programmers}\footnote{\textcolor{violet}{[Ben says: I'm unsure this is needed and naturally adds more text. Willing to accept...]}}
so it can be explored.
\sout{There are multiple ways to collect epidemiological data.}
\textcolor{violet}{In epidemology, there are multiple different formats the data can arrive in.}
\footnote{\textcolor{orange}{[Shannon suggests: "Epidemiological data are collected in many different formats."]} \textcolor{violet}{[Ben says: I see the point you're trying to make and made a new edit - but it's less connected to the previous sentence since "format" is the end.]}}
Sometimes individual records are collected, with times of different
states of the epidemic (infection, recovery, etc.) as well as individual
information like network structure, location, and sub-population
information. Other data collections focus on aggregate counts of
individuals in each epidemic state. In fact, many times only the number
of new infections at each time step (e.g.~weekly case counts) is
observed. Compartment totals (amounts of individuals in each state) are
then imputed from those case
counts\sout{ along with}\textcolor{orange}{and}\footnote{\textcolor{violet}{[Ben says: Declined. I'm unclear why we should. Is the sentence unclear? Maybe it's the way it's a compound sentence? - If so a rewrite would be better?]}}
other information about the disease and the population of interest. In
\pkg{EpiCompare}, we focus on understanding the overall impact of an
outbreak at the aggregate/population level, which allows for streamlined
examination of overall trends of an epidemic.

To help the practitioner examine epidemics from an aggregate/ population
lens, we provide a function called \texttt{agents\_to\_aggregate()}.
This function transforms data about individual/agents' initial entry
into each state (e.g.~start of infection, start of recovery, etc.) to an
aggregate view of how many individuals were in a state at a given time.
There are often situations where
\textcolor{violet}{\sout{grouping} aggregating}\footnote{\textcolor{violet}{[Ben says: reason - connect to languare from sentence before.]}}
agents into subpopulations
(e.g.~sub\sout{populations}\textcolor{orange}{ groups}\footnote{\textcolor{violet}{[Ben says: declined. I'm unclear why we'd do this.]}}
defined by age or sex) can highlight different aggregate level trends.
For example, research by \citet{rvachev1985,anderson1992,worby2015}
develop state-based models that account for differing disease dynamics
in different subpopulations. In \pkg{EpiCompare}, we facilitate
subpopulation analysis by combining the function
\pkg{dplyr}::\texttt{group\_by()} and \texttt{agent\_to\_aggregate()} to
provide aggregation
\sout{at a}\textcolor{orange}{by}\footnote{\textcolor{violet}{[Ben says: declined. unclear about this change. Also would it not be "by groups"? Orignial seems to flow more.]}}
group level.

The \texttt{agents\_to\_aggregate()} function is flexible and can deal
with a wide range of information about each individual.
\textcolor{violet}{\sout{It can,} In fact, this function can} account
for infinitely many states. This functionality allows the practitioner
to aggregate information relative to common states
(e.g.~``Susceptible'', ``Infectious'', and ``Recovered'') as well as
more complex states (e.g.~``Exposed'', ``iMmune'', ``Hospitalized'').
Additionally, \texttt{agents\_to\_aggregate()} permits indicators for
death/exit and birth/entry dates. Overall, this function is a powerful
tool for pre-processing data,
\textcolor{orange}{and it lowers the barrier for entry into data analysis for less experienced practicioners.}\footnote{\textcolor{orange}{[Shannon says: I added this in theme with 'highlighting a point of entry']} \textcolor{violet}{[Ben says: I'm unclear about this comment but I'm find with the addition...]}}

@@

\textcolor{violet}{\sout{With raw data, "Getting to know" our} In the early stages of a project, getting to know the}\footnote{\textcolor{orange}{[Shannon suggested: "Getting to know" our]} \textcolor{violet}{[Ben says: even though I was the original one with the quotes - one should always stray away from it. I kept the implicit connection to the section we're in given I'm not sure people are reading the titles super well.]}}
data currently means figuring out useful combinations of visualizations
\textcolor{violet}{\sout{,}and} numerical summaries and
\sout{\sout{subsets}\textcolor{orange}{groupings}}\textcolor{violet}{exploring different groupings of the data}\footnote{\textcolor{violet}{[Ben says: the action "figuring out" and "groupings" was a bit unclear what actually was going to happen - so I changed it.]}}.
\textcolor{violet}{\sout{An expert coder has many ways to successfully explore the data in an aggregate lens using }}\texttt{agents\_to\_aggregate()}\textcolor{violet}{\sout{. For less experienced coders, \pkg{EpiCompare} also includes tools to rapidly explore data that has three epidemic states.} An expert coder can start from }
\texttt{agents\_to\_aggregate()}
\textcolor{violet}{to successfully accomplish EDA in many ways, but \pkg{EpiCompare} also includes tools that allow a novice coder to rapidly explore data, as long as there three unique epidemiological states (like the SIR model).}\footnote{\textcolor{violet}{[Ben says: I'm reverting to the old text - it's much clearer. - happy to have a a discussion on it. The crossed out text didn't capture what an expert coder was really going to do and how that differed.]}}
Building on \textcolor{violet}{\sout{the tools in}} \pkg{ggplot2} and
\pkg{ggtern} \textcolor{violet}{packages}, \pkg{EpiCompare}`s
\texttt{geom\_aggregate()} provides a rapid way to explore different
subpopulations' experiences of an epidemic
\citep{Wickham2016, Hamilton2018}.
\textcolor{violet}{The function }\texttt{geom\_aggregate()}
\textcolor{violet}{provides a visualization tool to holistically examine aggregate level information across different subpopulations by visualizing each subpopulation's epidemic trajectory in the three-dimensional state space.}
\footnote{\textcolor{violet}{[Original text: "By combiing the ideas behind agent2aggregate for three-state models to examine subpopulation trajcetories in 2d simplex space."]} \textcolor{orange}{[Shannons says: I got rid of the end of this sentence because I think it was putting multiple ideas in one sentence.]}\textcolor{violet}{[Ben says: I'm unclear why this warrants just deleting it. I've provided a newly written sentence...]}}
Visualization tools for three-state models were developed because (1)
SIR models are some of the most common and basic epidemic state-based
models and (2) our three-dimensional simplex representation of these
epidemics emphasizes a ``time-invarance'' representation of the data
(for a refresher see Section \ref{sec:time-invariant}).

@@

\textcolor{violet}{[Ben says: think about this section and if it highlights that we can bring in outside models...]}

After getting a good sense of what a past or current epidemic looks like
with EDA, the next step is often model fitting and/or simulations.
\sout{In this step and the next step (post-processing), we discuss how to \textcolor{orange}{easily include external models and simulations originating outside into the \pkg{EpiCompare} data analysis pipeline.}}\textcolor{violet}{In this step and the next step (post-proessing), we highlight how practitioners can pair models and simulations of epidemics from outside of \pkg{EpiCompare} with analysis and simulation tools in \pkg{EpiCompare}.}\footnote{\textcolor{violet}{[Ben says: the original rewrite didn't seem to clear - specifically in how the practitioner would be using outside models in this step.]}}
While \pkg{EpiCompare} does not focus on fitting model(s) to data, we do
provide some flexible functions for simulation of basic discrete-time
epidemic-state models.
\textcolor{violet}{These functions simulation individual-level information based on practitioner estimated transition rates between states and}
can be combined with \texttt{agents\_to\_aggregate()} to view these
simulations through an aggregate lens. The function
\texttt{simulate\_SIR\_agents()} simulates a basic SIR epidemic with
user inputs for the number of simulations, the initial number in each
state, the infection and recovery parameters \((\beta, \gamma\)), and
the total number of discrete time steps. This function allows for easy
access to SIR model analysis and comparison. Beyond SIR models, the
function \texttt{simulate\_agents()} takes as input a user-specified
state-transition matrix and other epidemic parameters to allow the user
to create simulations for an outbreak with \textit{any} number of states
and any number of transitions among them. This flexibility in states can
be used to also reflect group-based dynamics. In turn, this allows for
users to explore the space of models in an intuitive way without getting
bogged down by too much mathematical detail. For consistency, we have
made output from \texttt{simulate\_agents()} and
\texttt{simulate\_SIR\_agents()} compatible with
\texttt{agents\_to\_aggregate()} so aggregate information may easily be
accessed.

@@

\textcolor{violet}{[Ben says: I think we should remind the reader that we care more about simulations, in order to compare fitted models between themselves and the true epidemics.]}

\textcolor{violet}{[Ben says: this replaces the first paragraph below]}

If the practitioner wishes to compare models-to-observations or even
models-to-models, they needs to post-process their models and
simulations to disseminate the results in an easily digestable format.
In general, post-processing of modeling and simulation consists of
making summary statistics, plots, and tables.
\textcolor{violet}{Model \sout{The}} summaries can be very complex, and
as a result, a number of epidemic modeling \textbackslash proglang\{R\}
packages return \textcolor{violet}{\sout{a}} special class
\textcolor{violet}{objects}. The special
class\textcolor{violet}{\sout{es} objects} often contain a plethora of
information from residuals, model diagnostics, input parameters, and
more. While incredibly useful, these special classes can be difficult
for novice coders to \textcolor{violet}{\sout{navigate} handle}.

@@

\textcolor{orange}{[Shannon says: Here Ben talks about filament compression and tidy\_dist mats, etc.]}
\textcolor{violet}{[Ben says: not currently thinking about including tidy\_dist stuff - will need to think about this as it is including in the pipeline 2 image...]}
\footnote{\textcolor{violet}{[Ben says: are these comments still relevant?]}}

To utilize simulations of epidemics in later time-invariant analysis we
also provide a function to convert temporally defined epidemics to
filamental representations. Specifically, we provide the function
\texttt{filament\_compression()} to convert simulation(s) to filaments
as expressed by presenting the epidemic as a ordering of some common
fixed number of points so that they are equally spaced along the
original path in the proportional state space.

\textcolor{orange}{[Shannon says: Shannon's attempt at above paragraph is below..  I tried to more smoothly connect to previous paragraph and then kinda copped out at trying to reword the filament description by just referring back to the previous section.]}

\pkg{EpiCompare} also provides a tool to convert time-dependent epidemic
simulations into their time-invariant filamental representations.
Specifically, \texttt{filament\_compression()} converts simulations to
filaments (see Section \ref{sec:time-invariant})
\textcolor{violet}{\sout{so practitioners can view model simulations and results through a time-invariant lens.}which allows practitioner to later apply time-invariant tools to these compressed epidemiological objects.}\footnote{\textcolor{violet}{[Ben says: I worry about this statement - it is very broad / seems to claim a lot but not very clearly...]}}
These tools were developed to provide another natural entry point into
the \pkg{EpiCompare} data analysis pipeline for situations where
modeling and analysis is already completed and practitioners are looking
for simple and transparent tools to help understand and disseminate
results.

@@

\textcolor{violet}{[Ben says: I didn't look at this section - it looks like your comments are more "let's" talk about this and not suggestions / feedback.]}

\textcolor{orange}{Finally, \pkg{EpiCompare} can be used the last step of the data analysis pipeline with its comparison and assessment utility functions.}
As introduced in Section \ref{sec:beyond-r0-sir} there's a
\sout{lot of}\textcolor{orange}{much} potential for time-invariant tools
to help compare and assess epidemics and models/simulations. In
\pkg{EpiCompare} we provide a set of comparison and assessment tools for
models that extend beyond the standard performance metrics (e.g.~mean
squared error or AIC) and focus on assessing the structural information
the models capture. This approaches work well on models where
\sout{online} one ``cycle'' of the epidemic has occurred (no recovered
individuals have been susceptible
again)\footnote{\textcolor{violet}{[Ben says: Shannon - do you think this is clear / a desirable way to define this - we define it slightly differently in section 2.2.]}\textcolor{orange}{Shannon says I don't think I understand what you are trying to say there.  We should chat about it.}}.
Epidemics are complex objects, and we provide tools to create prediction
regions
\textcolor{orange}{with differing desired characteristics}\footnote{\textcolor{orange}{Shannon says: I want to connect epidemics being complex to the fact that prediction is hard and not all prediction regions tell you the same thing}}
from simulated epidemics. For three-state epidemic models, we provide
the \texttt{ggplot}/\texttt{ggtern} extension
\texttt{geom\_prediction\_band()} which creates a prediction region
around the top \(1-\alpha\) proportion
{[}\textcolor{orange}{good place for Ben paper cite?}{]} of the
simulations (where the simulations treated as filaments). In
\pkg{EpiCompare} we also provide these prediction regions for epidemic
models with with more than three states. The functions
\texttt{create\_convex\_hull\_structure()} and
\texttt{create\_delta\_ball\_structure()} create different geometric
representations of prediction regions for any state-based model. For
both of these geometric objects, we provide functions to check if a path
is contained (\texttt{contained()}) and the ability to assess the
Hausdorff distance between prediction regions based on simulations from
different model (\texttt{hassdorf\_dist()}).
\footnote{\textcolor{violet}{[Ben says: should we discuss the details of geom\_prediction\_bands more? ]}\textcolor{orange}{[Shannon says: I don't think so, best left to the vignette and data example]}}

We also provide functions to calculate the ``extremeness'' of a true
epidemic {[}\textcolor{orange}{trajectory?}{]} compared to simulated
epidemics via the equi-distance filamental trajectory representation as
mentioned in Section \ref{sec:beyond-r0-sir}. Specifically, functions
like \texttt{distance\_pseudo\_density\_function()} can calculate a
pseudo-density estimate of the true epidemic relative to simulated ones.
Functions \texttt{distance\_depth\_function()} and
\texttt{local\_distance\_depth\_function()} provide depth scores that
suggest how geometrically central an epidemic is to simulations.
\footnote{\textcolor{violet}{[Ben says: should we define these more in this paragraph? Introducted in 2.2. as well and not defined.]}\textcolor{orange}{[Shannon says: I'd throw a citation or two but again limit the detail.]}}

\textcolor{violet}{[Ben says: Replaced with paragraphs above.]}
Comparison and assessment of model fit or comparisons of one model to
another model can be performed in a variety of ways including mean
square error, AIC, plots, and more. Perhaps the most useful tool
\pkg{EpiCompare} has to offer to the expert, for comparison and
assessment of models, is in its post-processing tools which create a
standard output. It is then a matter of writing a script or function
made for that standard output to assess the results from multiple models
in the way the user
desires\footnote{\textcolor{violet}{[Ben says: Shannon, doesn't this below in the previous section?, I might drop this paragraph except for the introduction sentence - is it really true that the standardization is most valuable?]}\textcolor{orange}{I agree with you now that this section is nice and filled in.  Let's drop this paragraph.}}.

\textcolor{violet}{[Ben says: Replaced with paragraphs above.]} However,
for those who like more concrete tools, \pkg{EpiCompare} offers
functions to compare prediction regions to one another including
\texttt{geom\_prediction\_band()} (which plots the region), and
\texttt{create\_\{convex\_hull,delta\_ball\}\_structure()}(which returns
the \texttt{R} output for the given structure), and \texttt{contained()}
(which allows the user to determine if one set of points is contained in
a prediction band). Additionally, we offer ways to determine if model
outputs are compatible with one another, that is how extreme one output
is to another. \textcolor{orange}{Ben says something about distance}

>>>>

In this section, we present the tools implemented in \pkg{EpiCompare}
and explain how they aid in the data analysis pipeline. In Fig.
\ref{fig:pipeline2}, we illustrate how our package's functions fit into
the data analysis pipeline introduced in Fig. \ref{fig:pipeline}. All
front-facing functions in \pkg{EpiCompare} are aimed to be as
user-friendly as possible. We also focus on providing the user
``tidyverse'' style functions, that encourage piping objects from one
function to the next and follow clear ``verb'' naming schemes
\citep{Wickham2019}. Although users can incorporate \pkg{EpiCompare}
into any step in the data analysis pipeline, there are two primary
points of entry. The first point of entry is the very beginning with
pre-processing and visualizing raw data, and the second point of entry
is after modeling and simulation. Figure \ref{fig:pipeline2} captures
these different paths, and we highlight how to leverage \pkg{EpiCompare}
functionalities in the subsections below.

@@

The first step of most data analysis is ``cleaning'' the raw data so it
can be explored. Before data can be explored, they must be collected.
Raw data can appear in many different formats. Sometimes individual
records are collected, with times of different states of the epidemic
(infection, recovery, etc.) as well as individual information like
network structure, location, and sub-population information. Other data
collections focus on aggregate counts of individuals in each epidemic
state. In fact, many times only the number of new infections at each
time step (e.g.~weekly case counts) is observed. Compartment totals
(amounts of individuals in each state) are then imputed from those case
counts other information about the disease and the population of
interest. In \pkg{EpiCompare}, we focus on understanding the overall
impact of an outbreak at the aggregate/population level, which allows
for streamlined examination of overall trends of an epidemic.

To help the practitioner examine epidemics from an aggregate/population
lens, we provide a function called \texttt{agents\_to\_aggregate()}.
This function transforms data about individual/agents' initial entry
into each state (e.g.~start of infection, start of recovery, etc.) to an
aggregate view of how many individuals were in a state at a given time.
There are often situations where aggregating agents into subpopulations
(e.g.~subpopulations defined by age or sex) can highlight different
aggregate level trends. For example, research by
\citet{rvachev1985,anderson1992,worby2015} develop state-based models
that account for differing disease dynamics in different subpopulations.
In \pkg{EpiCompare}, we facilitate subpopulation analysis by combining
the function \pkg{dplyr}::\texttt{group\_by()} and
\texttt{agent\_to\_aggregate()} to provide aggregation at a
subpopulation level.

\textcolor{orange}{Besides aiding subpopulation analysis,}
\texttt{agents\_to\_aggregate()} can deal with a wide range of
information about each individual. In fact, this function account for
infinitely many states. This functionality allows the practitioner to
aggregate information relative to common states (e.g.~``Susceptible'',
``Infectious'', and ``Recovered'') as well as more complex states
(e.g.~``Exposed'', ``iMmune'', ``Hospitalized''). Additionally,
\texttt{agents\_to\_aggregate()} permits indicators for death/exit and
birth/entry dates. Overall, this function is a powerful tool for
pre-processing data.

@@

In the early stages of a project, familiarizing oneself with the data
usually means figuring out useful combinations of visualizations and
numerical summaries of the data
\textcolor{orange}{both at population and subpopulation level.} An
expert coder can start with \texttt{agents\_to\_aggregate()} to
successfully accomplish EDA in many ways. \pkg{EpiCompare} also includes
tools that allow a novice coder to rapidly explore data, provided there
three unique epidemiological states (like in the SIR model). Building on
\pkg{ggplot2} and \pkg{ggtern} packages, \pkg{EpiCompare}'s
\texttt{geom\_aggregate()} provides a rapid way to explore how different
subpopulations experience of an epidemic
\citep{Wickham2016, Hamilton2018}. The function
\texttt{geom\_aggregate()} provides a visualization tool to holistically
examine aggregate level information across different subpopulations by
visualizing each subpopulation's epidemic trajectory in the
three-dimensional state space. Visualization tools for three-state
models were developed because (1) SIR models are some of the most common
and basic epidemic state-based models and (2) our three-dimensional
simplex representation of these epidemics emphasizes a
``time-invarance'' representation of the data (for a refresher see
Section \ref{sec:time-invariant}).

@@

After getting a sense of what a past or current epidemic looks like with
EDA, often the next step in the data analysis pipeline is model fitting
and/or simulation. In this step and the next step (post-proessing), we
highlight how practitioners can pair models and simulations of epidemics
from outside of \pkg{EpiCompare} with analysis and simulation tools in
\pkg{EpiCompare}. While \pkg{EpiCompare} does not focus on fitting
models to data, we do provide some flexible functions for simulation of
basic discrete-time epidemic-state models. These functions simulate
individual-level information based on practitioner estimated transition
rates between states and can be combined with
\texttt{agents\_to\_aggregate()} to view these simulations through an
aggregate lens. The function \texttt{simulate\_SIR\_agents()} simulates
a basic SIR epidemic with user inputs for the number of simulations, the
initial number in each state, the infection and recovery parameters
\((\beta, \gamma\)), and the total number of discrete time steps. This
function allows for easy access to SIR model analysis and comparison.
Beyond SIR models, the function \texttt{simulate\_agents()} takes as
input a user-specified state-transition matrix and other epidemic
parameters to allow the user to create simulations for an outbreak with
\textit{any} number of states and any number of transitions among them.
This flexibility in states can be used to also reflect group-based
dynamics. In turn, this allows for users to explore the space of models
in an intuitive way without getting bogged down by too much mathematical
detail. For consistency, we have made output from
\texttt{simulate\_agents()} and \texttt{simulate\_SIR\_agents()}
compatible with \texttt{agents\_to\_aggregate()} so aggregate
information may easily be accessed.

@@

If practitioners wish to compare models-to-observations or even
models-to-models, they needs to post-process their models and
simulations to disseminate the results in an easily digestible format.
In general, post-processing of modeling and simulation consists of
making summary statistics, plots, and tables. Model output summaries can
be very complex, and as a result, a number of epidemic modeling
\proglang{R} packages return a special class. The special classes often
contain a plethora of information about residuals, model diagnostics,
input parameters, and more. While incredibly useful, these special
classes can be difficult for novice coders to handle.

@@

To utilize simulations of epidemics in time-invariant analysis, we also
provide a function to convert temporally defined epidemics to filamental
representations. Specifically, we provide the function
\texttt{filament\_compression()} to convert simulation(s) to filaments
as expressed by presenting the epidemic as an ordering of some common
fixed number of points so that they are equally spaced along the
original path in the proportional state space. These tools were
developed to provide another natural entry point into the
\pkg{EpiCompare} data analysis pipeline for situations where modeling
and analysis are already completed and practitioners are looking for
simple and transparent tools to help understand and disseminate results.

@@

Finally, in \pkg{EpiCompare} we provide a set of comparison and
assessment tools for model and simulation results that extend beyond the
standard performance metrics (e.g.~mean squared error or AIC).
Corresponding to Section \ref{sec:beyond-r0-sir}, \pkg{EpiCompare}
provides a set of time-invariant tools to compare and evaluate epidemic
models and simulations. We have found these tools to be specifically
applicable for situations where only one ``season'' or ``cycle'' of the
epidemic has occurred.

One tool we provide to assess models is through the creation of
geometric prediction regions, which are useful when we treat epidemics
like filaments. If there is a set of simulated epidemics from a model,
we can create a geometric prediction region for the expected trajectory
of the epidemic in the state space. For three-state epidemic models, we
provide the \texttt{ggplot}/\texttt{ggtern} extension
\texttt{geom\_prediction\_band()} which creates a prediction region
around the top \(1-\alpha\) proportion of the simulations. In this
visual setting, comparing this prediction to the true epidemic
trajectory or comparing the prediction regions defined by two different
models' simulations can be done with the `eye test.' In \pkg{EpiCompare}
we also provide these prediction regions for epidemic models with with
more than three states. The functions
\texttt{create\_convex\_hull\_structure()} and
\texttt{create\_delta\_ball\_structure()} create different geometric
representations of prediction regions for any dimensional state-based
model. For both of these geometric structures, we provide functions to
check if a path is contained (\texttt{contained()}) and the ability to
assess the Hausdorff distance between prediction regions based on
simulations from different model (\texttt{hausdorff\_dist()}).

We also provide functions to calculate the ``extremeness'' of a true
epidemic trajectory compared to simulated epidemics via the
equi-distance filamental trajectory representation as mentioned in
Section \ref{sec:beyond-r0-sir}. Specifically, functions like
\texttt{distance\_pseudo\_density\_function()} can calculate a
pseudo-density estimate of the true epidemic relative to simulated ones.
Functions \texttt{distance\_depth\_function()} and
\texttt{local\_distance\_depth\_function()} provide depth scores that
suggest how geometrically central an epidemic is to simulations.
